Developing a public preprint culture in biology

### 2012-10-11 ms.tex
minor edits

%%% TP Oct 11 2012
%%% Important to appeal to the young folks, while at the same time calling for
%%% more recognition of preprints. Feel free to rephrase, but don't remove!

@@

There are a number of reasons that biologists have not traditionally had a
culture of sharing preprints, many of which are based on common misconceptions
regarding the costs and benefits associated with the practice. For example, in contrast
to other fields there is a perception in biology that public preprints
make it easier to steal ideas. However, there is no evidence of this happening
in the numerous other fields that have adopted preprint servers, and since preprint
servers create a clear record of who had the idea first, and when, this
appears to be a largely unfounded concern. In other fields preprints serve the
opposite role, they allow straightforward establishment of precedence, letting
research lay claim to an idea thus preventing it from being "stolen".
%%% TP
%%% Most refs will ask for a ref at that point. At least, I will, but I'm so
%%% demanding that I'm part of why the review process sucks ;-)

>>>>

@@

There are a number of reasons that biologists have not traditionally had a
culture of sharing preprints, many of which are based on common misconceptions
regarding the costs and benefits associated with the practice. For example, in contrast
to other fields there is a perception in biology that public preprints
make it easier to steal ideas. However, there is no evidence of this happening
in the numerous other fields that have adopted preprint servers, and since preprint
servers create a clear record of who had the idea first, and when, this
appears to be a largely unfounded concern. In other fields preprints serve the
opposite role, they allow straightforward establishment of precedence, letting
research lay claim to an idea thus preventing it from being "stolen" \cite{gin11}
%%% TP
%%% Most refs will ask for a ref at that point. At least, I will, but I'm so
%%% demanding that I'm part of why the review process sucks ;-)
